Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-02 draft.tex

>>>>

The remainder of this manuscript is structured as follows.
We review Poincar\'e--Friedrichs constants for the gradient over convex domains in Section~\ref{section:poincare}.
We review basic notions of triangulations in Section~\ref{section:triangulations}.
We develop computable upper bounds for the Poincar\'e--Friedrichs constants for the gradient over face-connected triangulated domains in Section~\ref{section:gradient}.
We review the Sobolev spaces in vector calculus and the calculus of differential forms in Section~\ref{section:calculus}.
Regularized potential operators over convex sets are discussed in Section~\ref{section:potentialoperator}.
We then review the notion of shellable triangulations of manifolds in Section~\ref{section:advancedtriangulations}.
We construct an important geometric reflection operator in Section~\ref{section:extension}
and we finally provide computable upper bounds for Poincar\'e--Friedrichs constants for the exterior derivative over shellable triangulations in Section~\ref{section:poincarefriedrichs}.
We present numerical examples in Section~\ref{section:numericalexamples}.
